\subsection{Baselines}
\label{sec:baselines}

\paragraph{Classical baselines (RQ1).}
\label{sec:baselines:classical}
We compare RetroBug against classical baselines under 5-fold
stratified cross-validation on all 798 commits, using masked commit
messages at test time to reduce trivial keyword leakage.
The \textbf{keyword heuristic} labels a commit as Bug-Fix when the
masked message contains fix-related terms (e.g., \emph{fix},
\emph{bug}, \emph{patch})~\cite{tian2012identifying}.
\textbf{TF-IDF} vectorises the masked message (up to 5{,}000 unigram
and bigram features; $\mathrm{min\_df}=2$) and trains fold-specific
\textbf{LR}, \textbf{RF} (200 trees), or \textbf{XGB} classifiers.
\textbf{Hybrid features + LR} uses nine hand-crafted features (message
length, keyword counts, and diff statistics) with standardized
logistic regression.
\textbf{$k$NN retrieval} transfers the label of the nearest training
commit using the same \texttt{all-MiniLM-L6-v2} embedding model and
cosine similarity as RetroBug, but without LLM reasoning.

\paragraph{CCS baselines (RQ2).}
\label{sec:baselines:ccs}
For RQ2, we compare RetroBug against three zero-shot LLM baselines on
fold~0 ($n=160$), all using the commit-classification prompt of
Zeng~\textit{et al.}~\cite{zeng2025conventional} adapted to binary
Bug-Fix vs.\ Non-Bug-Fix classification.
Each baseline makes a single API call per commit with the masked
message and full git diff---no knowledge-base search, tools, or
multi-step reasoning---and returns a JSON label, confidence score, and
brief reasoning.
We evaluate \textbf{Claude Sonnet~4.5}, \textbf{GPT-4o}, and a locally
hosted \textbf{CodeLlama-13b-Instruct} model as an open-weight
comparison point.

Table~\ref{tab:baseline-summary} summarizes both baseline families.

\begin{table}[t]
\centering
\caption{Overview of baseline families and their inputs.}
\label{tab:baseline-summary}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Family} & \textbf{Method(s)} & \textbf{Input} & \textbf{Eval.} \\
\midrule
\multicolumn{4}{@{}l}{\textit{Classical baselines (RQ1)}} \\
\quad Heuristic    & Keyword           & Masked message       & 5-fold \\
\quad TF-IDF       & LR, RF, XGB       & Masked message       & 5-fold \\
\quad Hand-crafted & LR                & Engineered features  & 5-fold \\
\quad Retrieval    & $k$NN             & Embedding similarity & 5-fold \\
\midrule
\multicolumn{4}{@{}l}{\textit{CCS baselines (RQ2)}} \\
\quad Zero-shot LLM & Claude, GPT-4o, CodeLlama & Masked message + diff & Fold~0 \\
\bottomrule
\end{tabular}
\end{table}
