% RQ1 — Results subsection (prose + summary box)
% Requires: \usepackage{tcolorbox}
% Usage: \input{paper_tables/rq1_results_text.tex}
%         (table included via \input{paper_tables/rq1_results.tex} below)

\subsection{RQ1: RetroBug vs.\ Classical Baselines}
\label{sec:results:rq1}
% --------------------------------------------------------------

Table~\ref{tab:rq1} reports per-class precision, recall, F1, accuracy,
and MCC for all methods aggregated over 798 commits across five folds.
We compare RetroBug against three families of classical baselines:
a keyword heuristic, TF-IDF classifiers trained on masked commit
messages, hybrid models using nine hand-crafted diff and message
features, and a $k$NN retrieval baseline that transfers labels from
the nearest training commit in embedding space.

RetroBug achieves Bug-Fix F1~=~0.778 and MCC~=~0.703, outperforming
the best classical baseline---TF-IDF + LR on commit messages---by
27.8 Bug-Fix F1 points and 0.383 MCC points.
The improvement is driven primarily by recall: RetroBug recovers
90.5\% of all bug-fix commits compared with 53.8\% for TF-IDF + LR,
while also achieving higher Bug-Fix precision (0.682 vs.\ 0.467).
On the majority class, RetroBug maintains strong Non-Bug-Fix
performance (F1~=~0.909, precision~=~0.964), indicating that higher
bug-fix recall does not come at the cost of widespread non-bug
misclassification.

The MCC gap is the most informative single comparison.
TF-IDF + LR (message) achieves accuracy of 0.732 and Non-Bug-Fix F1
of 0.817, which appear reasonable in isolation, but its MCC of 0.319
reveals weak minority-class discrimination: the model misses more
than half of all bug-fixing commits.
Replacing LR with RF or XGB on the same TF-IDF features does not
close this gap---the best TF-IDF variant remains LR (Bug-Fix
F1~=~0.500), while RF and XGB reach only 0.403 and 0.416
respectively---confirming that the limitation is feature
expressiveness rather than classifier choice.

Hybrid-feature models expose a different failure mode.
Hybrid + LR achieves the highest Bug-Fix recall among classical
methods (0.724) by aggressively predicting Bug-Fix, but its Bug-Fix
precision collapses to 0.323 and overall accuracy falls to 0.553.
Hybrid + RF and Hybrid + XGB recover Non-Bug-Fix F1 ($\approx$0.79)
but sacrifice Bug-Fix recall (0.276--0.367), yielding Bug-Fix F1
scores below 0.37.
These results show that hand-crafted features alone cannot balance
precision and recall on this task.

$k$NN retrieval uses the same embedding model as RetroBug but applies
forward label transfer without backward reasoning or tool use.
It achieves MCC~=~0.264 and Bug-Fix F1~=~0.423---0.439 MCC points
and 35.5 F1 points below RetroBug---directly quantifying the gain of
agentic backward CBR over similarity-based label transfer.
Although $k$NN attains the second-highest Non-Bug-Fix F1 (0.835),
its Bug-Fix recall of 0.377 indicates that nearest-neighbor label
propagation misses nearly two-thirds of true bug-fix commits.

The keyword heuristic achieves the highest Non-Bug-Fix recall
(0.873) by classifying almost everything as Non-Bug-Fix, but its
Bug-Fix recall of 0.186 and MCC of 0.073 confirm that it is barely
better than random on the minority class.
Across all baselines, RetroBug is the only method that simultaneously
leads in Bug-Fix F1, Non-Bug-Fix F1, accuracy, and MCC.
All differences between RetroBug and baselines are statistically
significant ($p < 0.01$, Cohen's $d > 0.8$).

\input{paper_tables/rq1_results.tex}

\begin{tcolorbox}[colback=gray!8, colframe=gray!50,
  boxrule=0.5pt, arc=2pt, left=4pt, right=4pt,
  top=3pt, bottom=3pt]
\textbf{Answer to RQ1:}
RetroBug achieves Bug-Fix F1 of 0.778 ($\pm$0.027 across folds),
outperforming the best classical baseline (TF-IDF + LR, F1~=~0.500)
by 27.8 points, with recall rising from 0.538 to 0.905.
Compared to $k$NN retrieval (F1~=~0.423), RetroBug improves by 35.5
points, indicating that backward reasoning and tool use add value
beyond similarity-based label transfer.
\end{tcolorbox}
