% RQ2 — Results subsection (prose + summary box)
% Requires: \usepackage{tcolorbox}
% Usage: \input{paper_tables/rq2_results_text.tex}
%         \input{paper_tables/rq2_results.tex}

\subsection{RQ2: RetroBug vs.\ Zero-Shot LLM Baselines}
\label{sec:results:rq2}
% --------------------------------------------------------------

Table~\ref{tab:rq2} compares RetroBug with three zero-shot LLM baselines
on fold~0 ($n=160$).
All baselines receive the same inputs---a masked commit message and the
full git diff---and produce a single-pass binary label without knowledge-base
retrieval, backward reasoning, or tool use.
Claude Sonnet~4.5 and GPT-4o follow the conventional commit-classification
prompt of Zeng~\textit{et al.}~\cite{zeng2025conventional}; CodeLlama-13b
uses an equivalent JSON-structured prompt with prose fallback parsing.

RetroBug achieves Bug-Fix F1~=~0.776 and MCC~=~0.698, outperforming every
zero-shot baseline on all five reported metrics.
The strongest zero-shot competitor is GPT-4o (F1~=~0.629, MCC~=~0.493),
followed by Claude Sonnet~4.5 (F1~=~0.598, MCC~=~0.446) and CodeLlama-13b
(F1~=~0.431, MCC~=~0.171).
Relative to GPT-4o, RetroBug improves Bug-Fix F1 by 14.7 points and MCC
by 0.205 points; relative to Claude, the gains are 17.8 and 0.252 points
respectively.

The performance gap is driven primarily by \emph{precision}.
All three zero-shot models exhibit a Bug-Fix bias: they achieve high recall
(0.625--0.800) but low precision (0.329--0.571), misclassifying a large
share of non-bug commits as bug-fixes.
Claude Sonnet~4.5, for example, labels 35 of 120 non-bug commits as
Bug-Fix (precision 0.478), while still recovering 32 of 40 true bug-fix
commits (recall 0.800).
CodeLlama-13b amplifies this pattern most severely: it predicts Bug-Fix
for 76 commits but only 25 are correct (precision 0.329), yielding accuracy
of just 0.585 despite moderate recall (0.625).
GPT-4o balances the trade-off best among zero-shot models (precision
0.571, recall 0.700), but still falls 16.2 precision points below
RetroBug (0.733).

RetroBug's advantage over single-pass prompting indicates that multi-step
backward CBR, knowledge-base retrieval, and structured diff analysis add
value beyond exposing the same evidence to a capable LLM in one shot.
The agent recovers 33 of 40 bug-fix commits (recall 0.825) while limiting
false positives to 12 of 120 non-bug commits---a precision--recall profile
that none of the zero-shot baselines match.
We evaluate LLM baselines on fold~0 only due to API cost and inference
latency; RetroBug results on the same fold are directly comparable because
they use the identical 160-commit test split.

\input{paper_tables/rq2_results.tex}

\begin{tcolorbox}[colback=gray!8, colframe=gray!50,
  boxrule=0.5pt, arc=2pt, left=4pt, right=4pt,
  top=3pt, bottom=3pt]
\textbf{Answer to RQ2:}
On fold~0, RetroBug (Bug-Fix F1~=~0.776, MCC~=~0.698) outperforms the
best zero-shot LLM baseline, GPT-4o (F1~=~0.629, MCC~=~0.493), by 14.7
F1 points and 0.205 MCC points.
Zero-shot models achieve competitive recall but suffer from low Bug-Fix
precision (0.329--0.571), whereas RetroBug combines high recall (0.825)
with substantially higher precision (0.733).
These results show that agentic backward CBR and tool use improve
classification beyond single-pass LLM prompting on the same inputs.
\end{tcolorbox}
