% RQ3 — Results subsection (prose + summary box)
% Requires: \usepackage{tcolorbox}
% Usage: \input{paper_tables/rq3_results_text.tex}
%         \input{paper_tables/rq3_results.tex}

\subsection{RQ3: Cross-Fold Stability and Per-Class Balance}
\label{sec:results:rq3}
% --------------------------------------------------------------

Table~\ref{tab:rq3-retrobug} reports RetroBug's per-class precision,
recall, and F1 on each of the five stratified cross-validation folds,
together with fold-wise accuracy and MCC.
RQ3 asks whether agentic backward CBR maintains stable performance
across data splits and whether it balances Bug-Fix and Non-Bug-Fix
classification rather than over-fitting to the majority class.

Across all folds, RetroBug achieves mean Bug-Fix F1 of
0.778~($\pm$0.027), Non-Bug-Fix F1 of 0.909~($\pm$0.015), and MCC
of 0.705~($\pm$0.035).
Bug-Fix F1 ranges from 0.729 (fold~3) to 0.804 (fold~1), a spread of
7.5 points, indicating consistent performance despite variation in
the underlying repository and commit mix of each test split.
Non-Bug-Fix F1 is even more stable ($\sigma = 0.015$), remaining above
0.883 on every fold.
This low cross-fold variance compares favorably with classical
baselines: TF-IDF + LR exhibits Bug-Fix F1 of 0.500~($\pm$0.050) and
$k$NN retrieval 0.420~($\pm$0.065), both with wider fold-to-fold
swings despite lower absolute performance.

The per-class breakdown reveals how RetroBug sustains this balance.
Bug-Fix recall is consistently high across all folds
(0.825--0.975; mean~=~0.904~$\pm$~0.049), meaning the agent
recovers the vast majority of true bug-fix commits in every split.
Bug-Fix precision shows greater fold-level variation
(0.614--0.733; mean~=~0.686~$\pm$~0.046), reflecting that false-positive
rate depends more on the specific commits in each test fold.
Fold~3 is the most challenging: Bug-Fix precision drops to 0.614 and
MCC to 0.641, driven by 22 false-positive predictions among
120 non-bug commits, while recall remains strong at 0.897.
Folds~1 and~2 represent the most favorable conditions, each reaching
Bug-Fix F1~$\geq$~0.800 and MCC~$\geq$~0.732.

On the Non-Bug-Fix side, RetroBug achieves near-ceiling precision
(0.939--0.990; mean~=~0.965~$\pm$~0.016), confirming that the agent
rarely mislabels a non-bug commit when it predicts Non-Bug-Fix.
Non-Bug-Fix recall is lower (0.817--0.900; mean~=~0.860~$\pm$~0.033)
because the agent's high Bug-Fix recall necessarily accepts some
false-positive bug-fix predictions; however, this recall remains
well above the Non-Bug-Fix recall of hybrid-feature baselines that
sacrifice the majority class to chase Bug-Fix commits.

Aggregated over all 798 commits, RetroBug achieves Non-Bug-Fix F1 of
0.909 and Bug-Fix F1 of 0.778 (macro F1~=~0.843).
Relative to the best classical baseline (TF-IDF + LR), this
represents gains of 9.2 points on Non-Bug-Fix F1 and 27.8 points on
Bug-Fix F1 simultaneously---a balanced profile that no classical
method matches.
Table~\ref{tab:confusion} confirms this at the aggregate level:
RetroBug produces 180 true positives and 515 true negatives against
only 84 false positives and 19 false negatives over the full
5-fold evaluation.

\input{paper_tables/rq3_results.tex}

\begin{tcolorbox}[colback=gray!8, colframe=gray!50,
  boxrule=0.5pt, arc=2pt, left=4pt, right=4pt,
  top=3pt, bottom=3pt]
\textbf{Answer to RQ3:}
RetroBug maintains stable cross-fold performance (Bug-Fix
F1~=~0.778~$\pm$~0.027; Non-Bug-Fix F1~=~0.909~$\pm$~0.015) with
lower variance than TF-IDF + LR ($\pm$0.050) and $k$NN ($\pm$0.065).
High Bug-Fix recall (0.904~$\pm$~0.049) is consistent across all
folds, while Non-Bug-Fix precision remains near-ceiling
(0.965~$\pm$~0.016).
RetroBug improves both classes over the best classical baseline
(+9.2 Non-Bug-Fix F1, +27.8 Bug-Fix F1), demonstrating stable and
balanced classification rather than majority-class bias.
\end{tcolorbox}
